Supporting Information

### 2021-12-12 ms/ms.Rmd
updated Makefile

**Results** Contrary to our adapative hypothesis, we found no evidence that genetic variation in germination rate contributed to variation in early survival. Across populations, southern populations in both gardens germinated earlier and survived more.

@@

**Keywords:** cline, genotypic selection, germination, *Mimulus*, reciprocal transplant

>>>>

**Results** Contrary to our adaptive hypothesis, we found no evidence that genetic variation in germination rate contributed to variation in early survival. Across populations, southern populations in both gardens germinated earlier and survived more.

@@

**Keywords:** cline; genotypic selection; germination; *Mimulus*; reciprocal transplant

### 2021-12-12 ms/ms.tex
updated Makefile

@@

\textbf{Results} Contrary to our adapative hypothesis, we found no evidence that genetic variation in germination rate contributed to variation in early survival. Across populations, southern populations in both gardens germinated earlier and survived more.

@@

\textbf{Keywords:} cline, genotypic selection, germination, \emph{Mimulus}, reciprocal transplant

@@

\[V_G = 4~\sigma_{\mathrm{parent}}\]
Using \(\sigma_{\mathrm{parent}}\) rather than \(\sigma_{\mathrm{sire}}\) is more powerful because it uses all of the data, but assumes that maternal and paternal effects are negligible. We estimated \(\sigma_{\mathrm{parent}}\) and other parameters using a Bayesian mixed effects model. We describe the general approach here and provide detail specific to germination rate and survival below. We fit the model in \emph{Stan} (\protect\hyperlink{ref-stan_development_team_stan_2021}{Stan Development Team, 2021}) using \textbf{cmdstanr} version (\protect\hyperlink{ref-gabry_cmdstanr_2021}{Gabry and Češnovar, 2021}). \emph{Stan} calculates the posterior distribution of the model using the Hamiltonian Monte Carlo algorithm, which is similar to the more widely used Markov Chain Monte Carlo, but is faster and more efficient at sampling for many applications (\protect\hyperlink{ref-monnahan_faster_2017}{Monnahan et al., 2017}). We used weakly informative normally distributed priors for parameters that affect the trait mean (intercepts and coefficients) and half-Cauchy priors for variance parameters. Weakly informative priors are strongly recommended for complex mixed models (\protect\hyperlink{ref-mcelreath_statistical_2016}{McElreath, 2016}). We ran 4 parallel chains for 1000 warmup iterations, 1000 sampling iterations, and a thinning interval of 1. This configuration allowed parameters to converge, which we defined as the convergence diagnostic \(\hat{R} < 1.05\) and an effective sample size \(>1000\) (\protect\hyperlink{ref-vehtari_rank-normalization_2021}{Vehtari et al., 2021}). We inspected posterior predictive plots to assess model adequacy using the \texttt{pp\_check} function from the \emph{R} package \textbf{bayesplot} version 1.8.1 (\protect\hyperlink{ref-gabry_visualization_2019}{Gabry et al., 2019}). We used the posterior median for point estimates and calculated uncertainty with the 95\% quantile intervals from the posterior distribution. \emph{Stan} and \emph{R} code are available on GitHub (\url{https://github.com/cdmuir/mimulus-germination}) and will be archived on Zenodo upon publication. Data will be deposited on Dryad upon publication.

@@

The vast majority of seeds germinated in 1-2 weeks, but northern populations took a few days longer on average. 4206 out of 5321 plugs (79.0\%) had germinants in the North cohort; 5114 out of 5328 plugs (96.0\%) had germinants in the South cohort. South cohort seedlings also germinated about one day faster (mean = 7.7, median = 7) than the North cohort (mean = 8.9, median = 8). After accounting for cohort and block effects, southern populations consistently germinate faster (Fig. \ref{fig:mean-traits}a). For example, seeds from the slowest population (Rock Creek) germinated \(2.9~(95\%~\text{CI}~[2.0-3.8])\) days slower than the fastest population (West Fork Mojave River). The discretized log-normal distribution was an adequate model of germination rate based on the similarity of the posterior predictions to the observed data (Fig. \ref{fig:pp_check}).

Fewer plants survived over winter in the North garden than in the South garden (65.5\% versus 94.2\%). In both gardens, southern populations survived more often than northern populations even after accounting for block effects (Fig. \ref{fig:mean-traits}b). For example, in the North garden, we estimated that plants originating from the most southern population, Sweetwater River, survived \(80.4\%~(95\%~\text{CI}~[71.4\%-88.2\%])\) of the time compared to \(51.8\%~(95\%~\text{CI}~[39.7\%-67.0\%])\) for the most northern population Rock Creek. Similarly, in the South garden the local population from Sweetwater River survived \(95.1\%~(95\%~\text{CI}~[90.7\%-97.3\%])\) of the time compared to \(85.5\%~(95\%~\text{CI}~[74.7\%-91.2\%])\) for Rock Creek. The average temperature was warmer than the historical normal from 1961-1990, especially for the winter season in the south garden (Fig. \ref{fig:climate})

@@

The genetic variation in germination rate within populations of \emph{M. cardinalis} is similar to the genetic differences between them (Fig. \ref{fig:h2-germ}a). The between-population variance in the log-mean germination rate is \(0.021~(95\%~\text{CI}~[-0.053-0.088)]\) greater than that within populations, but the confidence intervals include 0. The environmental variance \(V_\text{E}\) is greater than \(V_\text{G}\), resulting in a moderate heritability \(H^2\) (Fig. \ref{fig:h2-germ}b). In contrast, there is virtually no genetic variance in winter survival (\(p_\text{surv}\)) in either garden, resulting in heritabilities that are effectively 0 (Fig. \ref{fig:h2-surv}). There is some variation between populations, but it is substantially less than the unexplained environmental variance in both gardens (Fig. \ref{fig:h2-surv}). Parameter estimates and confidence intervals for all variance components and heritabilities are given in Table \ref{tab:vc_table_germ} for germination rate and Table \ref{tab:vc_table_surv} for winter survival.

>>>>

\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

@@

\textbf{Results} Contrary to our adaptive hypothesis, we found no evidence that genetic variation in germination rate contributed to variation in early survival. Across populations, southern populations in both gardens germinated earlier and survived more.

@@

\textbf{Keywords:} cline; genotypic selection; germination; \emph{Mimulus}; reciprocal transplant

@@

\[V_G = 4~\sigma_{\mathrm{parent}}\]
Using \(\sigma_{\mathrm{parent}}\) rather than \(\sigma_{\mathrm{sire}}\) is more powerful because it uses all of the data, but assumes that maternal and paternal effects are negligible. We estimated \(\sigma_{\mathrm{parent}}\) and other parameters using a Bayesian mixed effects model. We describe the general approach here and provide detail specific to germination rate and survival below. We fit the model in \emph{Stan} (\protect\hyperlink{ref-stan_development_team_stan_2021}{Stan Development Team, 2021}) using \textbf{cmdstanr} version (\protect\hyperlink{ref-gabry_cmdstanr_2021}{Gabry and Češnovar, 2021}). \emph{Stan} calculates the posterior distribution of the model using the Hamiltonian Monte Carlo algorithm, which is similar to the more widely used Markov Chain Monte Carlo, but is faster and more efficient at sampling for many applications (\protect\hyperlink{ref-monnahan_faster_2017}{Monnahan et al., 2017}). We used weakly informative normally distributed priors for parameters that affect the trait mean (intercepts and coefficients) and half-Cauchy priors for variance parameters. Weakly informative priors are strongly recommended for complex mixed models (\protect\hyperlink{ref-mcelreath_statistical_2016}{McElreath, 2016}). We ran 4 parallel chains for 4000 warmup iterations, 4000 sampling iterations, and a thinning interval of 4. This configuration allowed parameters to converge, which we defined as the convergence diagnostic \(\hat{R} < 1.05\) and an effective sample size \(>1000\) (\protect\hyperlink{ref-vehtari_rank-normalization_2021}{Vehtari et al., 2021}). We inspected posterior predictive plots to assess model adequacy using the \texttt{pp\_check} function from the \emph{R} package \textbf{bayesplot} version 1.8.1 (\protect\hyperlink{ref-gabry_visualization_2019}{Gabry et al., 2019}). We used the posterior median for point estimates and calculated uncertainty with the 95\% quantile intervals from the posterior distribution. \emph{Stan} and \emph{R} code are available on GitHub (\url{https://github.com/cdmuir/mimulus-germination}) and will be archived on Zenodo upon publication. Data will be deposited on Dryad upon publication.

@@

The vast majority of seeds germinated in 1-2 weeks, but northern populations took a few days longer on average. 4206 out of 5321 plugs (79.0\%) had germinants in the North cohort; 5114 out of 5328 plugs (96.0\%) had germinants in the South cohort. South cohort seedlings also germinated about one day faster (mean = 7.7, median = 7) than the North cohort (mean = 8.9, median = 8). After accounting for cohort and block effects, southern populations consistently germinate faster (Fig. \ref{fig:mean-traits}a). For example, seeds from the slowest population (Rock Creek) germinated \(2.9~(95\%~\text{CI}~[2.1-3.9])\) days slower than the fastest population (West Fork Mojave River). The discretized log-normal distribution was an adequate model of germination rate based on the similarity of the posterior predictions to the observed data (Fig. \ref{fig:pp_check}).

Fewer plants survived over winter in the North garden than in the South garden (65.5\% versus 94.2\%). In both gardens, southern populations survived more often than northern populations even after accounting for block effects (Fig. \ref{fig:mean-traits}b). For example, in the North garden, we estimated that plants originating from the most southern population, Sweetwater River, survived \(80.4\%~(95\%~\text{CI}~[71.6\%-87.9\%])\) of the time compared to \(52.1\%~(95\%~\text{CI}~[39.9\%-65.8\%])\) for the most northern population Rock Creek. Similarly, in the South garden the local population from Sweetwater River survived \(95.2\%~(95\%~\text{CI}~[91.2\%-97.2\%])\) of the time compared to \(85.4\%~(95\%~\text{CI}~[75.9\%-90.8\%])\) for Rock Creek. The average temperature was warmer than the historical normal from 1961-1990, especially for the winter season in the south garden (Fig. \ref{fig:climate})

@@

The genetic variation in germination rate within populations of \emph{M. cardinalis} is similar to the genetic differences between them (Fig. \ref{fig:h2-germ}a). The between-population variance in the log-mean germination rate is \(0.023~(95\%~\text{CI}~[-0.050-0.091)]\) greater than that within populations, but the confidence intervals include 0. The environmental variance \(V_\text{E}\) is greater than \(V_\text{G}\), resulting in a moderate heritability \(H^2\) (Fig. \ref{fig:h2-germ}b). In contrast, there is virtually no genetic variance in winter survival (\(p_\text{surv}\)) in either garden, resulting in heritabilities that are effectively 0 (Fig. \ref{fig:h2-surv}). There is some variation between populations, but it is substantially less than the unexplained environmental variance in both gardens (Fig. \ref{fig:h2-surv}). Parameter estimates and confidence intervals for all variance components and heritabilities are given in Table \ref{tab:vc_table_germ} for germination rate and Table \ref{tab:vc_table_surv} for winter survival.

### 2021-12-12 ms/si.Rmd
updated Makefile

---
title: 'Supporting Information'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: ../template/annals-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

>>>>

---
title: 'Supporting Information'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: ../template/american-journal-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

### 2021-12-12 ms/si.tex
updated Makefile

\begin{longtable}[]{@{}ll@{}}
\caption{\label{tab:vc_table_germ} We decomposed variance in germination rate among populations (\(V_\text{pop}\)), additive genetic differences among individuals in the base population (\(V_\text{G}\)), experimental blocks within the greenhouse (Block), and residual environmental variance (\(V_\text{E}\)). The narrow-sense heritability \(h^2\) is \(V_\text{G} / (V_\text{G} + V_\text{E})\). Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Parameter & Median (95\% CI) \\
\midrule
\endhead
\(V_\text{pop}\) & 0.138 (0.0886--0.201) \\
\(V_\text{G}\) & 0.117 (0.0832--0.172) \\
Block & 0.0352 (0.0238--0.0553) \\
\(V_\text{E}\) & 0.266 (0.258--0.275) \\
\(H^2\) & 0.279 (0.213--0.365) \\
\bottomrule
\end{longtable}

@@

Sweetwater River & North & \(H^2\) & 0.00443 (0.0011--0.0142) \\
Sweetwater River & North & \(V_\text{E}\) & 0.18 (0.147--0.206) \\
Sweetwater River & North & \(V_\text{G}\) & 0.000733 (0.000205--0.00256) \\
Sweetwater River & North & \(V_\text{pop}\) & 0.00757 (0.00379--0.0112) \\
Sweetwater River & North & Block & 0.000733 (0.000205--0.00256) \\
West Fork Mojave River & North & \(H^2\) & 0.00469 (0.00117--0.0157) \\
West Fork Mojave River & North & \(V_\text{E}\) & 0.195 (0.156--0.219) \\
West Fork Mojave River & North & \(V_\text{G}\) & 0.000812 (0.000239--0.0033) \\
West Fork Mojave River & North & \(V_\text{pop}\) & 0.00757 (0.00379--0.0112) \\
West Fork Mojave River & North & Block & 0.000812 (0.000239--0.0033) \\
North Fork Middle Tule River & North & \(H^2\) & 0.00441 (0.0011--0.0141) \\
North Fork Middle Tule River & North & \(V_\text{E}\) & 0.172 (0.138--0.197) \\
North Fork Middle Tule River & North & \(V_\text{G}\) & 0.000675 (0.000198--0.00243) \\
North Fork Middle Tule River & North & \(V_\text{pop}\) & 0.00757 (0.00379--0.0112) \\
North Fork Middle Tule River & North & Block & 0.000675 (0.000198--0.00243) \\
Little Jamison Creek & North & \(H^2\) & 0.00531 (0.00127--0.016) \\
Little Jamison Creek & North & \(V_\text{E}\) & 0.219 (0.18--0.24) \\
Little Jamison Creek & North & \(V_\text{G}\) & 0.00109 (0.000289--0.00348) \\
Little Jamison Creek & North & \(V_\text{pop}\) & 0.00757 (0.00379--0.0112) \\
Little Jamison Creek & North & Block & 0.00109 (0.000289--0.00348) \\
Rock Creek & North & \(H^2\) & 0.00589 (0.00137--0.0186) \\
Rock Creek & North & \(V_\text{E}\) & 0.245 (0.225--0.249) \\
Rock Creek & North & \(V_\text{G}\) & 0.00142 (0.000341--0.00465) \\
Rock Creek & North & \(V_\text{pop}\) & 0.00757 (0.00379--0.0112) \\
Rock Creek & North & Block & 0.00142 (0.000341--0.00465) \\
Sweetwater River & South & \(H^2\) & 0.000937 (\(9.78 \times 10^{-5}\)--0.0043) \\
Sweetwater River & South & \(V_\text{E}\) & 0.0651 (0.0352--0.0998) \\
Sweetwater River & South & \(V_\text{G}\) & 6.5e-05 (\(5.35 \times 10^{-6}\)--0.000405) \\
Sweetwater River & South & \(V_\text{pop}\) & 0.00131 (0.000354--0.00283) \\
Sweetwater River & South & Block & 0.00518 (0.000938--0.0182) \\
West Fork Mojave River & South & \(H^2\) & 0.00102 (0.000104--0.00439) \\
West Fork Mojave River & South & \(V_\text{E}\) & 0.0683 (0.0398--0.106) \\
West Fork Mojave River & South & \(V_\text{G}\) & \(7.75 \times 10^{-5}\) (\(6.87 \times 10^{-6}\)--0.000461) \\
West Fork Mojave River & South & \(V_\text{pop}\) & 0.00131 (0.000354--0.00283) \\
West Fork Mojave River & South & Block & 0.00594 (0.00115--0.0244) \\
North Fork Middle Tule River & South & \(H^2\) & 0.00121 (0.00012--0.00486) \\
North Fork Middle Tule River & South & \(V_\text{E}\) & 0.0794 (0.0483--0.118) \\
North Fork Middle Tule River & South & \(V_\text{G}\) & 0.000105 (\(8.72 \times 10^{-6}\)--0.000634) \\
North Fork Middle Tule River & South & \(V_\text{pop}\) & 0.00131 (0.000354--0.00283) \\
North Fork Middle Tule River & South & Block & 0.00728 (0.0018--0.0269) \\
Little Jamison Creek & South & \(H^2\) & 0.00149 (0.000133--0.00549) \\
Little Jamison Creek & South & \(V_\text{E}\) & 0.088 (0.0512--0.124) \\
Little Jamison Creek & South & \(V_\text{G}\) & 0.000121 (\(1.16 \times 10^{-5}\)--0.000606) \\
Little Jamison Creek & South & \(V_\text{pop}\) & 0.00131 (0.000354--0.00283) \\
Little Jamison Creek & South & Block & 0.0103 (0.00227--0.0315) \\
Rock Creek & South & \(H^2\) & 0.00208 (0.00021--0.00792) \\
Rock Creek & South & \(V_\text{E}\) & 0.129 (0.0818--0.155) \\
Rock Creek & South & \(V_\text{G}\) & 0.000303 (\(3.09 \times 10^{-5}\)--0.00117) \\
Rock Creek & South & \(V_\text{pop}\) & 0.00131 (0.000354--0.00283) \\
Rock Creek & South & Block & 0.0208 (0.00488--0.05) \\

@@

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_pop_lm} Between-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on increased germination rate (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & 4.05 (3.09 -- 5.32) \\
North & slope & -0.455 (-0.642 -- -0.328) \\
South & intercept & 4.87 (3.82 -- 6.1) \\
South & slope & -0.354 (-0.528 -- -0.221) \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_ind_lm} Genotypic directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on increased germination rate (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & -0.00157 (-0.0349 -- 0.0273) \\
North & slope & -0.13 (-0.374 -- 0.0133) \\
South & intercept & 0.000634 (-0.0173 -- 0.0257) \\
South & slope & -0.00276 (-0.15 -- 0.138) \\
\bottomrule
\end{longtable}

>>>>

\begin{longtable}[]{@{}ll@{}}
\caption{\label{tab:vc_table_germ} We decomposed variance in germination rate among populations (\(V_\text{pop}\)), additive genetic differences among individuals in the base population (\(V_\text{G}\)), experimental blocks within the greenhouse (Block), and residual environmental variance (\(V_\text{E}\)). The narrow-sense heritability \(h^2\) is \(V_\text{G} / (V_\text{G} + V_\text{E})\). Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Parameter & Median (95\% CI) \\
\midrule
\endhead
\(V_\text{pop}\) & 0.139 (0.0877--0.203) \\
\(V_\text{G}\) & 0.116 (0.0839--0.168) \\
Block & 0.0354 (0.024--0.0556) \\
\(V_\text{E}\) & 0.266 (0.258--0.275) \\
\(H^2\) & 0.278 (0.215--0.358) \\
\bottomrule
\end{longtable}

@@

Sweetwater River & North & \(H^2\) & 0.00815 (0.00263--0.0205) \\
Sweetwater River & North & \(V_\text{E}\) & 0.181 (0.15--0.217) \\
Sweetwater River & North & \(V_\text{G}\) & 0.0015 (0.000512--0.00424) \\
Sweetwater River & North & \(V_\text{pop}\) & 0.00743 (0.0045--0.0115) \\
Sweetwater River & North & Block & 0.0015 (0.000512--0.00424) \\
West Fork Mojave River & North & \(H^2\) & 0.0087 (0.00274--0.0209) \\
West Fork Mojave River & North & \(V_\text{E}\) & 0.197 (0.159--0.226) \\
West Fork Mojave River & North & \(V_\text{G}\) & 0.00175 (0.000563--0.00463) \\
West Fork Mojave River & North & \(V_\text{pop}\) & 0.00743 (0.0045--0.0115) \\
West Fork Mojave River & North & Block & 0.00175 (0.000563--0.00463) \\
North Fork Middle Tule River & North & \(H^2\) & 0.00794 (0.00259--0.0202) \\
North Fork Middle Tule River & North & \(V_\text{E}\) & 0.174 (0.134--0.213) \\
North Fork Middle Tule River & North & \(V_\text{G}\) & 0.00141 (0.000464--0.00422) \\
North Fork Middle Tule River & North & \(V_\text{pop}\) & 0.00743 (0.0045--0.0115) \\
North Fork Middle Tule River & North & Block & 0.00141 (0.000464--0.00422) \\
Little Jamison Creek & North & \(H^2\) & 0.00963 (0.00296--0.0226) \\
Little Jamison Creek & North & \(V_\text{E}\) & 0.221 (0.191--0.24) \\
Little Jamison Creek & North & \(V_\text{G}\) & 0.0021 (0.000701--0.00546) \\
Little Jamison Creek & North & \(V_\text{pop}\) & 0.00743 (0.0045--0.0115) \\
Little Jamison Creek & North & Block & 0.0021 (0.000701--0.00546) \\
Rock Creek & North & \(H^2\) & 0.0101 (0.00307--0.0236) \\
Rock Creek & North & \(V_\text{E}\) & 0.241 (0.227--0.248) \\
Rock Creek & North & \(V_\text{G}\) & 0.00247 (0.000765--0.00586) \\
Rock Creek & North & \(V_\text{pop}\) & 0.00743 (0.0045--0.0115) \\
Rock Creek & North & Block & 0.00247 (0.000765--0.00586) \\
Sweetwater River & South & \(H^2\) & 0.000285 (5.3e-05--0.00326) \\
Sweetwater River & South & \(V_\text{E}\) & 0.0644 (0.0393--0.101) \\
Sweetwater River & South & \(V_\text{G}\) & \(2.07 \times 10^{-5}\) (\(2.95 \times 10^{-6}\)--0.000305) \\
Sweetwater River & South & \(V_\text{pop}\) & 0.00143 (0.000626--0.0028) \\
Sweetwater River & South & Block & 0.00528 (0.00155--0.0205) \\
West Fork Mojave River & South & \(H^2\) & 0.000316 (\(5.88 \times 10^{-5}\)--0.00328) \\
West Fork Mojave River & South & \(V_\text{E}\) & 0.0714 (0.0483--0.113) \\
West Fork Mojave River & South & \(V_\text{G}\) & \(2.41 \times 10^{-5}\) (\(4.54 \times 10^{-6}\)--0.000321) \\
West Fork Mojave River & South & \(V_\text{pop}\) & 0.00143 (0.000626--0.0028) \\
West Fork Mojave River & South & Block & 0.00645 (0.00201--0.0266) \\
North Fork Middle Tule River & South & \(H^2\) & 0.000356 (\(6.54 \times 10^{-5}\)--0.00334) \\
North Fork Middle Tule River & South & \(V_\text{E}\) & 0.0844 (0.0534--0.122) \\
North Fork Middle Tule River & South & \(V_\text{G}\) & \(3.42 \times 10^{-5}\) (\(5.84 \times 10^{-6}\)--0.000425) \\
North Fork Middle Tule River & South & \(V_\text{pop}\) & 0.00143 (0.000626--0.0028) \\
North Fork Middle Tule River & South & Block & 0.00894 (0.00264--0.031) \\
Little Jamison Creek & South & \(H^2\) & 0.000381 (\(7.29 \times 10^{-5}\)--0.00424) \\
Little Jamison Creek & South & \(V_\text{E}\) & 0.0934 (0.0606--0.13) \\
Little Jamison Creek & South & \(V_\text{G}\) & \(4.07 \times 10^{-5}\) (\(8.42 \times 10^{-6}\)--0.000513) \\
Little Jamison Creek & South & \(V_\text{pop}\) & 0.00143 (0.000626--0.0028) \\
Little Jamison Creek & South & Block & 0.0108 (0.00354--0.0353) \\
Rock Creek & South & \(H^2\) & 0.000525 (0.000104--0.00627) \\
Rock Creek & South & \(V_\text{E}\) & 0.131 (0.1--0.159) \\
Rock Creek & South & \(V_\text{G}\) & \(8.36 \times 10^{-5}\) (\(1.57 \times 10^{-5}\)--0.000972) \\
Rock Creek & South & \(V_\text{pop}\) & 0.00143 (0.000626--0.0028) \\
Rock Creek & South & Block & 0.0225 (0.00926--0.0511) \\

@@

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_pop_lm} Between-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on increased germination rate (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & 4.06 (3.09 -- 5.26) \\
North & slope & -0.456 (-0.629 -- -0.324) \\
South & intercept & 4.9 (3.84 -- 6.08) \\
South & slope & -0.355 (-0.53 -- -0.225) \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_ind_lm} Genotypic directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on increased germination rate (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & -0.0022 (-0.034 -- 0.0273) \\
North & slope & -0.131 (-0.371 -- 0.0122) \\
South & intercept & 0.000691 (-0.0176 -- 0.0266) \\
South & slope & -0.00177 (-0.14 -- 0.13) \\
\bottomrule
\end{longtable}
